\documentclass[margin,line,a4paper]{resume}

\usepackage[latin1]{inputenc}
\usepackage[english,danish]{babel}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{url}

\usepackage[colorlinks=true, a4paper=true, pdfstartview=FitV,
linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}

\begin{document}
    {\sc \Large Curriculum Vitae -- Leonard Botha}
    \begin{resume}
        \vspace{0.5cm}

        \section{\mysidestyle Personal Information}
            Leonard Botha\\
            Tel: +27 79 524 1596\\
            Email: \href{mailto:leonardzbotha@gmail.com}{leonardzbotha@gmail.com}\\
            GitHub: \href{http://github.com/lzbotha}{http://github.com/lzbotha}\\

        \section{\mysidestyle Education}
            \begin{description}
                \item[Free University of Bozen-Bolzano] (October 2016 - March 2017)
                    Foreign exchange in order to work with specialists on MSc thesis topic, as well as taking some classes.

                \item[University of Cape town] (2016 - 2018)\\
                    MSc in Computer Science with a focus on developing a Bayesian Description Logic, $\mathcal{BALC}$. This research is based on the existing Bayesian DL $\mathcal{BEL}$, and extends the classical Description Logic $\mathcal{ALC}$ with Bayesian Networks.

                \item[University of Cape Town] (2015) \\
                    BSc Honours in Computer Science. Thesis on ``Extraction of  walkable regions from 3D scanned mesh data''.
                    Which can then be used for pathfinding applications in both virtual and real world applications.

                \item[University of Cape Town] (2012 - 2014) \\
                    BSc in Computer Science, Mathematics, and Game Development.

                \item[Somerset College](2007 - 2011)\\
                    Distinctions in Mathematics, Information Technology, Physical Sciences and English.
            \end{description}


        \section{\mysidestyle Work and Internships}
            \begin{description}
            	\item[HealthQ Technologies] (Jan 2018 - present) \\
                    Worked as a Data Engineer (until Oct 2018) attached to the analytics team. Responsibilities included: scaling of existing algorithms, validation of results and algorithms, as well development of new ML models. \\
                    Currently working as a Research Engineer (Oct 2018 - present). Responsibilities include: productionization of ML models, scaling of existing solutions, as well as developing and improving ML models.

            	\item[University of Cape Town] (June - July 2017) \\
            		Teaching assistant for the third year undergraduate Computer Science course at UCT.

            	\item[University of Cape Town] (April - May 2017) \\
            		Tutoring the Honours level course Logics for Artificial Intelligence.

                \item[Fullstack] (12th January 2016 - 31st July 2016) \\
                    Work on ingesting social media data into the Hadoop ecosystem. Data was ingested from media sources using the NiFi pipeline, with Hive used to provide a view over the data once stored on HDFS. Work also included using fuzzy matching to connect social media accounts from different platforms to a single user.

                \item[Quick Internet Services] (12th June - 30th July 2015) \\
                    Work on developing the front-end of the desktop application using the PyQt framework.

                \item[TravelGround] (16th June - 18th of July, 2014) \\
                    Built an email parser service to categorize company-client correspondences based on booking information. As well as some work on backend similarity matching between holiday locations.

            \end{description}
        
        \section{\mysidestyle Publications}    
            \begin{description}
                \item Botha, Leonard, Thomas Meyer, and Rafael Penaloza. "The Bayesian Description Logic BALC." (2018).
                \item Botha, Leonard, Thomas Meyer, and Rafael Penaloza. "A Bayesian Extension of the Description Logic ALC" (in press).
            \end{description}

        \section{\mysidestyle Technologies previously worked with}
        	\begin{description}
	        	\item [Programming, Scripting, and Query Languages] Java, Python, C, Go
	 			\item [Operating Systems] Linux, Mac
	 			\item [Other Technologies] Hadoop, NiFi, Docker, TensorFlow, TensorFlow Serving
	 		\end{description}

       	\section{\mysidestyle References}
            Available on request
    \end{resume}
\end{document}
\grid
